\vspace{-0.5cm} XSGRB - The X-shooter GRB afterglow sample

### 2017-10-26 document/XSGRB_sample.tex
Small edit

We additionally provide an estimate of the continuum for all the spectra
presented here. We have developed an algorithm that attempts to automatically
find the continuum placement along with the error on the continuum estimate. For
each arm,

@@

We have
adopted the following naming convention GRB*OB*.fits

In this section we describe the data format. Similar to what is done in \citet{Lopez2016}

>>>>

We additionally provide an estimate of the continuum for all the spectra
presented here. For this, we have developed an algorithm that attempts to automatically
finds the continuum placement along with the error on the continuum estimate.

@@

%We have
%adopted the following naming convention GRB*OB*.fits
%
%
%In this section we describe the data format. Similar to what is done in \citet{Lopez2016}
%
%
